When Subgraph Isomorphism is Really Hard, and Why This Matters for Graph Databases

### 2017-11-10 paper/paper.tex
Density -> Probability
Underline

\subsection{A Phase Transition when Varying Pattern Edge Density}

@@

\subsection{Phase Transitions when Varying Pattern and Target Edge Densities}

@@

Various general principles have been considered when designing variable- and value-ordering
heuristics for backtracking search algorithms---one of these is to try to maximise the expected
number of solutions inside any subproblem considered during search \citep{DBLP:conf/cp/GentMPSW96}.
This is usually done by cheaper surrogates, rather than direct calculation. When branching, both LAD
and Glasgow pick a variable with fewest remaining values in its domain: doing this will generally
reduce the first part of the $\langle Sol \rangle$ equation (i.e.\ $t^p$) by as little as possible.
When two or more domains are of equal size, LAD breaks ties lexicographically, whereas Glasgow will
pick a variable corresponding to a pattern vertex of highest degree. This strategy was determined
empirically, but could have been derived from the $\langle Sol \rangle$ formula: picking a pattern
vertex of high degree will make the remaining pattern subgraph sparser, which will decrease the
exponent in the second half of the formula, maximising the overall value. LAD does not apply a
value-ordering heuristic, but Glasgow does: it prefers target vertices of highest degree.  Again,
this was determined empirically, but it has the effect of increasing $\langle Sol \rangle$ by
leaving as many vertices as possible available for future use. The search strategy used by VF2, in
contrast, is based around preserving connectivity, which gives very little discrimination except on
the sparsest of inputs.

>>>>

\subsection{A Phase Transition when Varying Pattern Edge Probability}

@@

\subsection{Phase Transitions when Varying Pattern and Target Edge Probabilities}

@@

Various general principles have been considered when designing variable- and value-ordering
heuristics for backtracking search algorithms---one of these is to try to maximise the expected
number of solutions inside any subproblem considered during search \citep{DBLP:conf/cp/GentMPSW96}.
This is usually done by cheaper surrogates, rather than direct calculation. When branching, both LAD
and Glasgow pick a variable with fewest remaining values in its domain: doing this will generally
reduce the first part of the $\langle Sol \rangle$ equation (i.e.\ $t^{\underline{p}}$) by as little
as possible.  When two or more domains are of equal size, LAD breaks ties lexicographically, whereas
Glasgow will pick a variable corresponding to a pattern vertex of highest degree. This strategy was
determined empirically, but could have been derived from the $\langle Sol \rangle$ formula: picking
a pattern vertex of high degree will make the remaining pattern subgraph sparser, which will
decrease the exponent in the second half of the formula, maximising the overall value. LAD does not
apply a value-ordering heuristic, but Glasgow does: it prefers target vertices of highest degree.
Again, this was determined empirically, but it has the effect of increasing $\langle Sol \rangle$ by
leaving as many vertices as possible available for future use. The search strategy used by VF2, in
contrast, is based around preserving connectivity, which gives very little discrimination except on
the sparsest of inputs.
